\section{Problems and Issues}
\noindent
When approaching the project, we have faced many problems. They can be divided into three main categories.
\subsection{understand the data}
\noindent
The first main problem that we have encountered is about understanding the data. Although we have a large dataset, there is no specific file that introduces the data structure or explain the meaning of the variables. Due to the lack of documentation of these relative information, we have spent much time reading through the paper and searching the website. Even so, there are still some problems unsolved: for example, we had no ideas about the variable called "PTval" in the behavior data and did not use it for our analysis. Meanwhile, since the data we are analyzing is fMRI data and we are all unfamiliar with its format and processing procedure, therefore, in the beginning, we found that the technical field studies are difficult to understand. 
\noindent
The insufficient description of the analysis methods also made us hard to reproduce the work. For example,  there are no descriptions about the QA section. When we are trying to reproduce the plots or calculate certain statistics, we can not get the exact results: the plots have the same shapes and patterns but the values on the y-axis are more than two times smaller than those in the QA report. As a result, we doubted that they might perform some transformations on the data set but did not mention them in the paper. We also attempted to do a generalized logistic regression for the behavioral data by including gender and age of each subjects, but there was no specific guidance on how to perform this.

\subsection{Coding}
\noindent
The second main problem that we have faced is about the coding. In order to assure the reproducibility of our analysis, we need to do everything from the terminal, instead of simple point and click. We write a lot of functions, scripts and tests to download, unzip, load the files and travel through different folders.
\noindent
We also use Git to do version control. However, it might cause some conflicts or misunderstandings when we just merge the pull requests. In order to avoid these situations, we keep track of others’ code, try to add more descriptions to our code and review others' pull request more carefully.

\subsection{Data Analysis}
\noindent
The hardest problems come from the data analysis. Our image data and behavior data for each run and each individual are in different folders, so sometimes it's hard to work on data across subjects and runs.
Meanwhile, the length of behavior data, which is 239, does not match the length of image data, which is only 86. Therefore, when we tried to combine them together and check if there are some linear relationships between them, we didn't how how to deal with the difference. If we fill in NA, we will lose much information; if we fill in 0, it is meaningless to run a linear regression that have many zeros in it.
\noindent
We also have many questions regards to the convolution. In the lecture or our homework, the convolution matrix is given to us, but now, we need to create a convolution matrix by ourselves. We are also unable to determine the parameters of the gamma distribution for the HRF. Most of online papers are using gamma quadratic (2 gamma functions + intercept term) and the common practice is to use 6 and 12 and an intercept of -0.35; however, the results are not reasonable for our project. We will continue working on it, try different parameters and find more online sources.

